\documentclass{article}


% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
\PassOptionsToPackage{sort, numbers, compress}{natbib}
% before loading neurips_2022


% ready for submission
% \usepackage{neurips_2024}


% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2022}


% to compile a camera-ready version, add the [final] option, e.g.:
     \usepackage[final]{neurips_2024}


% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib]{neurips_2022}


\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
%\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors


\usepackage{makeidx}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{graphics}
\usepackage{graphicx}
\allowdisplaybreaks
\thispagestyle{empty}
\usepackage{framed}

\usepackage{subfigure}

\usepackage{framed}
\usepackage{mathrsfs}
\usepackage{enumerate}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usepackage[all]{xy}
\usetikzlibrary{shapes}
\usetikzlibrary{decorations.markings}
%\usepackage{hyperref}
\usepackage{multirow}
\usepackage{bm}

\definecolor{mydarkblue}{rgb}{0,0.08,0.45}
\usepackage[colorlinks=true,
    linkcolor=mydarkblue,
    citecolor=mydarkblue,
    filecolor=mydarkblue,
    urlcolor=mydarkblue,
    pdfview=FitH]{hyperref}

\usepackage[T1]{fontenc}

% Tim's Commands
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cP}{\mathcal P}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cL}{\mathcal L}
\newcommand{\K}{\mathbb K}
\newcommand{\N}{\mathbb N}
\newcommand{\Z}{\mathbb Z}
\newcommand{\R}{\mathbb R}
\newcommand{\Q}{\mathbb Q}

%\newcommand{\max}{\operatornamewithlimits{\mbox{argmax}\,}}

\newcommand{\Aff}{\mathrm{Aff}\,}
\newcommand{\Abb}{{\textrm Abb}}

\newcommand{\adj}{{\textrm adj}\;}
\newcommand{\aff}{\mathrm{aff}\,}
\newcommand{\Def}{\mathrm{def}\;}
\newcommand{\End}{\mathrm{End}}

\newcommand{\Aut}{\mathrm{Aut}}
\newcommand{\GL}{\text{GL}}

\newcommand{\Hom}{\textrm Hom}





\newcommand{\bS}{\mathbb{S}}
\newcommand{\Sn}{\bS^n}




\newcommand{\bE}{\mathbb E}

\newcommand{\cN}{\mathcal N}

\newcommand{\B}{\mathbb B}
\newcommand{\bB}{\mathbb B}
%\newcommand{\C}{\mathbb C}

\newtheorem{proposition}{Proposition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]

\def\argmin{ \mathrm{argmin}}

\def\argmax{ \mathrm{argmax}}

\newcommand{\bd}{\mathrm{bd}\,}
\newcommand{\bi}{\binom}
\newcommand{\Char}{\mathrm{char}}
\newcommand{\cone}{\mathrm{cone}\;}
\newcommand{\co}{\mathrm{conv}\,}
\newcommand{\core}{\mathrm{core}\,}
\newcommand{\cl}{\mathrm{cl}\,}
\newcommand{\clco}{\overline{\mathrm{conv}}\,}
\newcommand{\diag}{\mathrm{diag}\,}
\newcommand{\dist}{\mathrm{dist}\,}
\newcommand{\dom}{\mathrm{dom}\,}
\newcommand{\conjug}{\;\overset{*}{\longleftrightarrow }\;}
\newcommand{\epi}{\mathrm{epi}\,}
\newcommand{\ext}{\mathrm{ext}\,}
\def\elim{{\textrm e-}\hspace{-0.5pt}\lim}
\def\glim{{\textrm g-}\hspace{-0.5pt}\lim}
\newcommand{\gph}{\mathrm{gph}\,}
\newcommand{\grad}{\mathrm{grad}\;}
\newcommand{\id}{\mathrm{id}\,}
\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\ind}{\mathrm{Ind}\,}
\newcommand{\inter}{\mathrm{int}\,}
\newcommand{\im}{\mathrm{rge}\,}
\newcommand{\Ima}{\mathrm{Im}}
\newcommand{\lev}{\mathrm{lev}}
\def\Lim{\mathop{{\textrm Lim}\,}}
\def\Liminf{\mathop{{\textrm Lim}\,{\textrm inf}}}
\def\Limsup{\mathop{{\textrm Lim}\,{\textrm sup}}}
\newcommand{\nul}{\mathrm{nul}\,}
\newcommand{\p}{\partial}
\newcommand{\rge}{\mathrm{rge}\,}

\newcommand{\rank}{\mathrm{rank}\,}

\newcommand{\Real}{\mathrm{Re}}
\newcommand{\sgn}{\mathrm{sgn}?}
\newcommand{\rbar}{\overline{\mathbb R}}
\newcommand{\rp}{\mathbb R\cup \{+\infty\}}
\newcommand{\rbd}{\mathrm{rbd}\,}
\newcommand{\ri}{\mathrm{ri}\,}
\newcommand{\set}[2]{\left\{#1\,\left\vert\; #2\right.\right\}}

\newcommand{\Uni}{\mathrm{U}}
\newcommand{\Orth}{\mathrm{O}}
\newcommand{\SU}{\mathrm{SU}}
\newcommand{\SO}{\mathrm{SO}}

\newcommand{\spn}{\mathrm{span}\,}

\newcommand{\Sym}{\mathrm{Sym}\,}

\newcommand{\tr}{\mathrm{tr}\,}

\newcommand{\lin}{\mathrm{span}\,}

\newcommand{\AND}{\quad\mbox{and}\quad}
\newcommand{\IFF}{\quad\Longleftrightarrow\quad}

% definition of Cartesian products
\def\XX{\operatornamewithlimits{\mbox{\sf\large X}}}
\def\XXX{\operatornamewithlimits{\mbox{\sf\Large X}}}

\pagestyle{empty}

\usepackage[algoruled, linesnumbered, shortend, lined]{algorithm2e}
\usepackage{algpseudocode}

\SetAlgoSkip{bigskip}
\SetKwInput{Input}{Input\hspace{34pt}{ }}
\SetKwInput{Output}{Output\hspace{27pt}{ }}
\SetKwInput{Initialize}{Initialize\hspace{20pt}{ }}
\SetKwInput{Parameters}{Parameters\hspace{2pt}{ }}

\newcommand{\prox}{\text{prox}}

\title{Project Report - Image Deblurring}


% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.


\author{%
  Alexander Kakabadze \\
  Student ID: 123456789
  % examples of more authors
  \And
  Edmand Yu \\
  Student ID: 123456789\\
 \AND
 Lilian Yuan\\
 Student ID: 123456789\\
 \And
 Rahul Padmanabhan\\
 Student ID: 567894321\\ 
}

\include{macros}

\begin{document}

\maketitle


\begin{abstract}
  This project implements and compares several convex optimization algorithms for image deblurring and denoising.
  We present four different algorithms: Primal Douglas-Rachford Splitting (Spingarn's Method), Primal-Dual Douglas-Rachford Splitting, the alternating direction method of multipliers (ADMM) and the Chambolle-Pock Algorithm.
  Each method is implemented with consideration of computational efficiency and convergence properties.
  The algorithms handle various types of blur kernels, including Gaussian and motion blur, while incorporating different regularization terms such as L1, L2, and isotropic norms.
  Our implementation leverages modern computational tools including PyTorch for efficient tensor operations and automatic differentiation.
  The project includes tests to evaluate the performance of each algorithm in terms of convergence speed, image quality metrics, and computational efficiency.
  The results demonstrate the effectiveness of these convex optimization approaches in restoring degraded images while preserving important image features and textures.
\end{abstract}


\section{Introduction}

An image can be read as a function $f: \mathbb{R}^2 \to \mathbb{R}$ where the domain is the 2D space and the range is the set of real numbers.
In practice, it is a tensor of size $3 \times H \times W$ where $H$ and $W$ are the height and width of the image and the third dimension corresponds to the RGB channels.
Image deblurring is a common problem in computer vision (CV) and image processing with the aim to recover a sharp image from a blurred version of the image.
%TODO add the classical methods of deblurring
Classical methods of deblurring could be used when the blurring is not too severe and there is a need for real-time performance.
Newer methods of deblurring use deep learning to solve this problem as there is suboptimal performance of classical methods in complicated cases such as a strong motion blur\cite{al2012comprehensive}.
In this work, we focus on the classical methods of deblurring.
The blurring model is given by:
\begin{equation*}
  k \ast x + \eta = y
\end{equation*}
where $k$ is the blurring kernel, $x$ is the original image, $y$ is the blurred image, $\eta$ is the noise and $\ast$ denotes the 2D convolution operation.
There are several types of image blur, such as Gaussian blur, motion blur, mixed blur, out-of-focus blur, etc.
Some blurring kernels are spatially invariant, which means that the kernel is the same everywhere in the image.
In this work, we focus on the spatially invariant motion blur.
We focus on the case where the blurring kernel is known (termed as the \emph{non-blind} framework).


\section{Background}

\subsection{Types of blurring kernels}

%TODO add the types of blurring kernels


\subsection{Proximal operators}

% TODO add the proximal operators


\section{Algorithms}
In this section, we present the algorithms that we implemented.

\subsection{Primal Douglas-Rachford Splitting (Spingarn's Method)}
TODO

\subsection{Primal-Dual Douglas-Rachford Splitting}
TODO

\subsection{Alternating Direction Method of Multipliers (ADMM)}
TODO

\subsection{Chambolle-Pock Algorithm}
TODO

\section{Experiments}
TODO
\subsection{Metrics}
We used the following metrics to evaluate the performance of the algorithms:
\begin{itemize}
  \item Peak Signal-to-Noise Ratio (PSNR)\cite{korhonen2012peak}
  \item Structural Similarity Index (SSIM)\cite{wang2002universal}
  \item L1 norm
  \item L2 norm
\end{itemize}

\subsection{Convergence}
TODO
\subsection{Performance}
TODO
\subsection{Comparison}
TODO

\section{Conclusion}
TODO

\section{Future Work}
TODO


\newpage

\section*{Acknowledgments}
Please include a list of each person (with student ID) in your group
and write a paragraph \textbf{for each person} with exactly what they
did. Note that the Acknowledgment section does not count towards the
page limit.

Example Acknowledgments would look like:

\paragraph{David Hippocampus} (Student ID: 123456789) David did all
the work. He coded all the algorithms and wrote the majority of the
paper.

\paragraph{George Danzig} (Student ID: 11235712) He didn't do very
much work. Danzig was mostly focused on his other classes, namely
linear programming. 


\bibliographystyle{plainnat}
\bibliography{references.bib}

\medskip



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\appendix


\section{Appendix}


Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
This section will often be part of the supplemental material.


\end{document}
